Summary Statistics

### 2024-12-05 extensive_tests/draft-sumstat-vignette.Rmd
Updating changes in sumstats

>>>>

## Comparison of tree tips

### Frequency of Methylation State Changes at Single Sites

We compare the methylation state of single sites at the tree cherries. A cherry is a pair of leaf nodes (also called tips or terminal nodes) in a phylogenetic tree that share a direct common ancestor. In other words, if two leaves are connected to the same internal node and no other leaves are connected to that internal node, they form a cherry.

get_FChange_cherryData (uses find_cherries and cherry_diffs)
